\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape ABDULLAH SOBHY} \\ \vspace{1pt}
    \small
    \raisebox{-0.1\height}\faMapMarker\ Alexandria, Egypt ~
    \href{mailto:abdallahbs9393@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{abdallahbs9393@gmail.com}} ~
    \raisebox{-0.1\height}\faPhone\ (+20)155-032-8625 ~
    \href{https://linkedin.com/in/yourprofile}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}  ~
    \href{https://github.com/yourusername}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} ~
    \href{https://codeforces.com/profile/yourusername}{\raisebox{-0.2\height}\faCode\ \underline{Codeforces}}
    \vspace{-8pt}
\end{center}

\section{SUMMARY}
\begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
    Web Developer with strong foundations in Laravel, React, PHP, and MySQL, building secure, responsive, and scalable web applications. Experienced with authentication, CRUD, REST APIs, and modern front-end tooling. Passionate about clean code, performance, and delivering smooth user experiences.
    }}
\end{itemize}
\vspace{-16pt}

\section{SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
    \textbf{Frontend:} React, JavaScript (ES6+), TypeScript, HTML5, CSS3, Tailwind CSS, Bootstrap, Next.js, Vite \\
    \textbf{Backend:} PHP, Laravel (Sanctum for Auth), REST APIs, GraphQL, JWT \\
    \textbf{Database:} MySQL, SQL, Database Design \& Management \\
    \textbf{Tools \& Technologies:} Git, GitHub, Docker, Postman, Stripe API, Socket.io, Pusher \\
    \textbf{CMS:} WordPress, WooCommerce, Elementor, WPForms, YayCommerce \\
    \textbf{Programming Fundamentals:} Object-Oriented Programming (OOP), Data Structures \& Algorithms, C++, Java \\
    \textbf{Soft Skills:} Communication, Team Collaboration, Time Management, Problem Solving, Adaptability, Attention to Detail, Critical Thinking, Self-motivation \\
    \textbf{Languages:} Arabic, English
    }}
\end{itemize}
\vspace{-16pt}

\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
{Freelance Frontend Developer}{Oct 2024 -- Present}
{LMS Platform Project}{}
\resumeItemListStart
\resumeItem{Built a comprehensive LMS platform using React, Next.js, TypeScript, and Tailwind CSS for an educational institution.}
\resumeItem{Architected reusable codebase with 3 foundational file structures (types, services, hooks) ensuring maintainability and scalability.}
\resumeItem{Implemented role-based interfaces for 4 user types: Teacher, Assistant, Student, and Admin with distinct dashboards and permissions.}
\resumeItem{Optimized application performance through code splitting, lazy loading, and efficient state management.}
\resumeItemListEnd

\resumeSubheading
{Full-Stack Developer}{Sep 2024 -- Dec 2024}
{Edvance - ACE Platform | University Capstone Project}{}
\resumeItemListStart
\resumeItem{Developed a comprehensive platform combining job board and Learning Management System (LMS) using the ACE (Access to Careers \& Education) framework, bridging the gap between university students' academic skills and professional opportunities.}
\resumeItem{Architected and implemented full-stack solution with Next.js 15, React 19, TypeScript, Tailwind CSS (frontend) and Laravel 12, PHP 8.2+ (backend); designed normalized database schema with 50+ tables supporting 6 distinct user roles.}
\resumeItem{Built 100+ RESTful API endpoints for authentication, job postings, course management, applications, payments, and real-time features; integrated Laravel Sanctum for secure token-based authentication and role-based access control.}
\resumeItem{Integrated 8 third-party services: DIDIT for identity verification, Google Gemini AI for career mentoring, JSearch API for external job listings, Mailgun for academic email OTP verification, Jitsi for live streaming, Stripe \& PayPal for payments, and Pusher for real-time notifications.}
\resumeItem{Implemented advanced features including AI-powered CV analysis and job recommendations, web scraping for external job data, live video classes with attendance tracking, multi-language support (Arabic/English), and comprehensive notification system.}
\resumeItem{Collaborated with 4-member team following Agile methodology; delivered fully functional platform deployed on Vercel with complete API documentation, video presentation, and technical documentation; achieved seamless integration between academic learning and job placement systems.}
\resumeItemListEnd

\resumeSubheading
{Freelance WordPress Developer}{Sep 2024}
{ZidClean - Cleaning Services Platform}{}
\resumeItemListStart
\resumeItem{Developed a full-featured cleaning services platform for the Saudi Arabia market covering home, villa, pool, furniture, and AC cleaning services.}
\resumeItem{Built 150+ pages, including 120 SEO-optimized blog posts; implemented Google Search Console indexing and on-page SEO best practices.}
\resumeItem{Integrated Stripe and PayPal payment gateways with custom PHP modifications to payment plugins for localized checkout flow.}
\resumeItem{Customized Elementor layouts and form plugins with PHP backend modifications; delivered full project in 5 days under a tight deadline.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}

\section{EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading
{Bachelor of Computer Science}{2022 -- 2026}
{Alexandria University}{GPA: 3.69}
\resumeSubHeadingListEnd

\end{document}
